Transient Corotating Clumps Around Adolescent Low-Mass Stars From Four Years of TESS

### 2023-11-01 paper/ms.tex
update ms

With the effective temperatures and stellar radii from the SED fit, we
estimated the stellar masses by interpolating against the PARSEC
isochrones \citep[v1.2S;][]{2014MNRAS.444.2525C}.  The need for models
that incorporate some form of correction for \deleted{young, active }M dwarfs is
well-documented \citep[e.g.][]{2012ApJ...756...47S,2015ApJ...804..146D,2016A&A...593A..99F,2018AJ....155..225K,2019MNRAS.489.2615M,2020ApJ...891...29S}.
Plausible explanations for the disagreement between observed and
theoretical M dwarf colors and sizes include starspot coverage
\citep[e.g.][]{2017ApJ...836..200G} and \deleted{potentially }incomplete line
lists \citep[e.g.][]{2013A&A...556A..15R}.  In the PARSEC models,
\citet{2014MNRAS.444.2525C} performed an empirical correction to the
temperature--opacity relation drawn from the BT-Settl model
atmospheres, in order to match observed masses and radii of young
eclipsing binaries.  This is sufficient for our goal of estimating
stellar masses.  Given our estimates of $\{ \tilde{T}_{\rm eff},
\tilde{R}_\star, \tilde{t} \}$, and approximating their uncertainties
as Gaussian $\sigma_{\tilde{T}_{\rm eff}}$, $\sigma_{\tilde{R}_\star}$
and $\sigma_{\tilde{t}}$, we define a distance metric $\Delta$ to each
model PARSEC grid-point $\{ T_{\rm eff}, R_\star, t \}$ via
\begin{equation}
  \Delta^2 = 
  \left( \frac{\tilde{T}_{\rm eff} - T_{\rm eff}}{\sigma_{\tilde{T}_{\rm eff}}} \right)^2
  +
  \left( \frac{\tilde{R}_{\star} - R_{\star}}{\sigma_{\tilde{R}_{\star}}} \right)^2
  +
  \left( \frac{\tilde{t} - t}{\sigma_{\tilde{t}}} \right)^2,
\end{equation}
where the division by the uncertainties helps to assign equal
importance to each dimension.  The mass reported in
Table~\ref{tab:thetable} is the model mass that minimizes the
distance.  The reported uncertainties in the masses are based on
propagating the statistical uncertainties in the radii, temperatures,
and ages.

@@

\added{To explore the proximity of the dip and spot periods, we
generated synthetic light curves that superposed a sinusoid and a single
eclipse.  We imposed periods, amplitudes, sampling, and noise properties
similar to typical CPVs in Figure~\ref{fig:cpvs}.  We then tuned
the period of the eclipse signal to differ slightly from the
sinusoidal period, and processed the resulting synthetic signals
through the same period-finding routine to which we subjected the real data.
Provided the dip and sinusoid periods agreed to within $\approx$0.1\%, we found that
phase-folding on the dominant period (that of the larger-amplitude starspots)
yielded dip signals analogous to those in Figure~\ref{fig:cpvs}.  However
increasing the period difference beyond $\gtrsim$0.3\%, the dip signal quickly becomes
``smeared'' out and unidentifiable when phase-folding.  This
exercise highlights that our search was sensitive only to stars with dip
and spot periods that agreed to within a few parts per thousand.  
Some CPVs may exceed this threshold; we encourage
future work aimed at determining whether such stars exist.}

>>>>

With the effective temperatures and stellar radii from the SED fit, we
estimated the stellar masses by interpolating against the PARSEC
isochrones \citep[v1.2S;][]{2014MNRAS.444.2525C}.  The need for models
that incorporate some form of correction for \deleted{young, active }M dwarfs is
well-documented \citep[e.g.][]{2012ApJ...757..112B,2012ApJ...756...47S,2015ApJ...804..146D,2016A&A...593A..99F,2018AJ....155..225K,2019MNRAS.489.2615M,2020ApJ...891...29S}.
Plausible explanations for the disagreement between observed and
theoretical M dwarf colors and sizes include starspot coverage
\citep[e.g.][]{2017ApJ...836..200G} and \deleted{potentially }incomplete line
lists \citep[e.g.][]{2013A&A...556A..15R}.  In the PARSEC models,
\citet{2014MNRAS.444.2525C} performed an empirical correction to the
temperature--opacity relation drawn from the BT-Settl model
atmospheres, in order to match observed masses and radii of young
eclipsing binaries.  This is sufficient for our goal of estimating
stellar masses.  Given our estimates of $\{ \tilde{T}_{\rm eff},
\tilde{R}_\star, \tilde{t} \}$, and approximating their uncertainties
as Gaussian $\sigma_{\tilde{T}_{\rm eff}}$, $\sigma_{\tilde{R}_\star}$
and $\sigma_{\tilde{t}}$, we define a distance metric $\Delta$ to each
model PARSEC grid-point $\{ T_{\rm eff}, R_\star, t \}$ via
\begin{equation}
  \Delta^2 = 
  \left( \frac{\tilde{T}_{\rm eff} - T_{\rm eff}}{\sigma_{\tilde{T}_{\rm eff}}} \right)^2
  +
  \left( \frac{\tilde{R}_{\star} - R_{\star}}{\sigma_{\tilde{R}_{\star}}} \right)^2
  +
  \left( \frac{\tilde{t} - t}{\sigma_{\tilde{t}}} \right)^2,
\end{equation}
where the division by the uncertainties helps to assign equal
importance to each dimension.  The mass reported in
Table~\ref{tab:thetable} is the model mass that minimizes the
distance.  The reported uncertainties in the masses are based on
propagating the statistical uncertainties in the radii, temperatures,
and ages.

@@

\added{To explore the proximity of the dip and spot periods, we
generated synthetic light curves that superposed a sinusoid and a single
eclipse.  We imposed periods, amplitudes, sampling, and noise properties
similar to typical CPVs in Figure~\ref{fig:cpvs}.  We then tuned
the period of the eclipse signal to differ slightly from the
sinusoidal period, and processed the resulting synthetic signals
through the same period-finding routine to which we subjected the real data.
Provided the dip and sinusoid periods agreed to within $\approx$0.1\%, we found that
phase-folding on the dominant period (that of the larger-amplitude starspots)
yielded dip signals analogous to those in Figure~\ref{fig:cpvs}.  However,
increasing the period difference beyond $\gtrsim$0.3\%, the dip signal quickly becomes
``smeared'' out and unidentifiable when phase-folding.  This
exercise highlights that our search was sensitive only to stars with dip
and spot periods that agreed to within a few parts per thousand.  
Some CPVs may exceed this threshold; we encourage
future work aimed at determining whether such stars exist.}
